An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-08 main.tex
Remove table. 2.

Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
the number of outcomes between all strategy pairs.
Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
stochastic matches have less than 788 unique outcomes whilst the maximum number
is 971. This ensures that using a set of cached results from 1000 precomputed
matches is sufficient for the analysis taking place here.
% TODO is this true? the distribution also matters, not just the number of outcomes

@@

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{./tex/number_of_match_outcomes.tex}
        \caption{All matches}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{./tex/number_of_stochastic_match_outcomes.tex}
        \caption{Stochastic matches}
    \end{subfigure}%
    \caption{Summary statistics for the number of different match outcomes used
    as the cached results}
    \label{tbl:number_of_stochastic_match_outcomes}
\end{table}

>>>>

Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
the number of outcomes between all strategy pairs.
% TODO is this true? the distribution also matters, not just the number of outcomes
% TODO Good point, we could (if we wanted to) go down the line of checking
% specific distributions etc or perhaps we just remove and point at the good
% fits in the Validation section as a justification.

@@
